Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-06-22 write-ups/FSE/paper.tex
Getting ready for camera-ready.

\documentclass[parskip=half,sigconf,review, anonymous=true, acmcopyrightmode=none]{acmart}
\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}

@@

% lstlisting macros
\lstset{
  language=C, % choose the language of the code
  showspaces=false, % show spaces adding particular underscores
  showstringspaces=false, % underline spaces within strings
  showtabs=false, % show tabs within strings adding particular underscores
  tabsize=8, % sets default tabsize to 2 spaces
  captionpos=b, % sets the caption-position to bottom
  mathescape=true, % activates special behaviour of the dollar sign
  basicstyle=\footnotesize\tt,
  columns=fullfelxible,
  xleftmargin=2em,
  %commentstyle=\rmfamily\itshape,
  morekeywords={barrier,kernel,global,__device__,__syncthreads,__global__,bool,then,transmit},
  escapeinside={(*@}{@*)},
  numbers=left
}

>>>>

\documentclass[sigconf]{acmart}

%%% The following is specific to ESEC/FSE'17 and the paper
%%% 'Cooperative Kernels: GPU Multitasking for Blocking Algorithms'
%%% by Tyler Sorensen, Hugues Evrard, and Alastair F. Donaldson.
%%%
%%% If you see 'none' in the 'setcopyright' statement below,
%%% please first submit your publishing-rights agreement with ACM (follow link on submission page),
%%% and then visit the instructions page again (follow link in author-kit message)
%%% in order to copy the correct 'setcopyright' statement.  Please contact us in case of questions.
%%%
\setcopyright{none}
\acmDOI{10.1145/3106237.3106265}
\acmISBN{978-1-4503-5105-8/17/09}
\acmConference[ESEC/FSE'17]{2017 11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{September 4-8, 2017}{Paderborn, Germany} 
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

@@

% lstlisting macros
\lstset{
  language=C, % choose the language of the code
  showspaces=false, % show spaces adding particular underscores
  showstringspaces=false, % underline spaces within strings
  showtabs=false, % show tabs within strings adding particular underscores
  tabsize=8, % sets default tabsize to 2 spaces
  captionpos=b, % sets the caption-position to bottom
  mathescape=true, % activates special behaviour of the dollar sign
  basicstyle=\footnotesize\tt,
  columns=fullfelxible,
  xleftmargin=2em,
  %commentstyle=\rmfamily\itshape,
  morekeywords={barrier,kernel,global,__device__,__syncthreads,__global__,bool,then,transmit},
  escapeinside={//(*@}{@*)},
  numbers=left
}
